IRS-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design Under Nonlinear Harvester Model

### 2021-06-11 main.tex
:pencil: Add complexity analysis

				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1\label{co:irs_rank}}

@@

			which is not a Semidefinite Programming (SDP) due to the quadratic objective function \eqref{eq:I_irs_approx}. The remaining non-convexity of problem~\eqref{op:irs} origins from the rank-\num{1} constraint~\eqref{co:irs_rank} and we relax it to formulate a convex problem \cite{Luo2010}. The tightness of rank relaxation is verified below.

			\begin{proposition}\label{pr:relaxation}
				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by rank relaxation.
			\end{proposition}

@@

			Problem~\eqref{op:irs} after rank relaxation can be solved by existing optimization tools such as CVX \cite{Grant2008}. We update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}.
			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\bar{R},\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $I^{(i)}$ by \eqref{eq:I_irs}
					\Until $\lvert I^{(i)}-I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}. We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence. The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}.
			\begin{algorithm}[!t]
				\caption{GP: Waveform Amplitude and Splitting Ratio.}
				\label{al:gp}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_n,P,\sigma_n,\bar{R},\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
					\State Compute $R^{(0)},I^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Repeat
						\State $i \gets i + 1$
						\State Update $\{\gamma_{m_{\mathrm{I},n}}^{(i)},\gamma_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star},\boldsymbol{s}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			The GP Algorithm~\ref{al:gp} achieves local optimality with exponential computational complexity \cite{Chiang2005}. To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design. Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session. When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}
			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:I_irs_approx} should be maximized. To achieve any non-WIT point (i.e., $I \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The tightness of rank relaxation and local optimality are proved similar to Proposition~\ref{pr:relaxation} and \ref{pr:sca} thus omitted here.

@@

		\begin{subsection}{Block Coordinate Descent}
			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence. The steps are summarized in the BCD Algorithm~\ref{al:bcd}. For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}.
			\begin{algorithm}[!t]
				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
				\label{al:bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $I^{(i)}$ by \eqref{eq:I_waveform}
					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

			\begin{algorithm}[!t]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\delta,\rho,\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{proof}\label{pf:bcd}
				See Appendix~\ref{ap:bcd}
			\end{proof}
		\end{subsection}
	\end{section}

@@

			By applying rank constraint relaxation, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t. $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds. The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.

>>>>

				\addConstraint{\mathrm{rank}(\boldsymbol{\Phi})=1.\label{co:irs_rank}}

@@

			We then apply Semi-Definite Relaxation (SDR) to the unit-rank constraint \eqref{co:irs_rank} and formulate a Semi-Definite Programming (SDP) with approximation accuracy no greater than $\pi/4$ \cite{Luo2010}. In this specific case, we found the solution provided by CVX toolbox \cite{Grant2008} to \eqref{ob:irs}-\eqref{co:irs_sd} is always rank-\num{1}. This conclusion is summarized below.

			\begin{proposition}\label{pr:relaxation}
				Any optimal solution $\boldsymbol{\Phi}^\star$ to the relaxed passive beamforming problem~\eqref{ob:irs}--\eqref{co:irs_sd} is rank-\num{1} such that \eqref{co:irs_rank} is tight and no loss is introduced by SDR.
			\end{proposition}

@@

			In summary, we update $\boldsymbol{\Phi}^{(i)}$ until convergence, extract $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, and retrieve the phase shift by $\theta_l^{\star}=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$. The passive beamforming design is summarized in the SCA Algorithm~\ref{al:sca}, where the relaxed problem \eqref{ob:irs}--\eqref{co:irs_sd} involves a $(L+1)$-order positive semi-definite matrix variable and $(L+2)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:sca} is $\mathcal{O}\left(I_{\mathrm{SCA}}(L+2)^4 (L+1)^{0.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{SCA}}$ denotes the number of SCA iterations \cite{Luo2010}.

			\begin{algorithm}[!t]
				\caption{SCA: IRS Phase Shift.}
				\label{al:sca}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},\sigma_n,\boldsymbol{w}_{\mathrm{I/P},n},\rho,\bar{R},\epsilon$, $\forall n$
					\State Construct $\boldsymbol{V},\boldsymbol{M},\boldsymbol{M}_n,\boldsymbol{C}_{n},\boldsymbol{C}_{\mathrm{I/P},k}$, $\forall n,k$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\Phi}^{(0)}$
					\State Set $t_{\mathrm{I/P},k}^{(0)}$, $\forall k$ by \eqref{eq:t_k}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\Phi}^{(i)}$ by solving \eqref{ob:irs}--\eqref{co:irs_sd}
						\State Update $t_{\mathrm{I/P},k}^{(i)}$, $\forall k$ by \eqref{eq:t_k}
						\State Compute $I^{(i)}$ by \eqref{eq:I_irs}
					\Until $\lvert I^{(i)}-I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\Phi}^{\star}=\boldsymbol{\Phi}^{(i)}$
					\State Get $\bar{\boldsymbol{\phi}}^\star$ by eigen decomposition, $\boldsymbol{\Phi}^{\star}=\bar{\boldsymbol{\phi}}^\star(\bar{\boldsymbol{\phi}}^\star)^H$
					\State Set $\theta_l^\star=\arg(\bar{\phi}_l^\star/\bar{\phi}_{L+1}^\star)$, $\forall l$, $\boldsymbol{\phi}^{\star}=[e^{j\theta_1^\star},\dots,e^{j\theta_L^\star}]^H$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			With \eqref{eq:gamma_I} and \eqref{eq:gamma_P}, problem~\eqref{op:waveform_gp} can be solved by existing optimization tools such as CVX \cite{Grant2008}. We update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_\mathrm{P}^{(i)},\rho^{(i)}$ iteratively until convergence. The joint waveform amplitude and splitting ratio design is summarized in the GP Algorithm~\ref{al:gp}, which achieves local optimality at the cost of exponential computational complexity \cite{Chiang2005}.

			\begin{algorithm}[!t]
				\caption{GP: Waveform Amplitude and Splitting Ratio.}
				\label{al:gp}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_n,P,\sigma_n,\bar{R},\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\rho^{(0)}$
					\State Compute $R^{(0)},I^{(0)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
					\State Set $\{g_{m_{\mathrm{I},n}}^{(0)},g_{m_\mathrm{P}}^{(0)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Repeat
						\State $i \gets i + 1$
						\State Update $\{\gamma_{m_{\mathrm{I},n}}^{(i)},\gamma_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:gamma_I}, \eqref{eq:gamma_P}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by solving problem~\eqref{op:waveform_gp}
						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
						\State Update $\{g_{m_{\mathrm{I},n}}^{(i)},g_{m_\mathrm{P}}^{(i)}\}$, $\forall n$ by \eqref{eq:g_I}, \eqref{eq:g_P}
					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{s}_{\mathrm{I/P}}^{\star}=\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{s}_{\mathrm{I}}^{\star},\boldsymbol{s}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

		\begin{subsection}{Low-Complexity Adaptive Design}
			To facilitate practical SWIPT implementation, we propose two closed-form adaptive waveform amplitude schemes by combining WF and SMF in the time and power domains. For WIT, the optimal WF strategy assigns the amplitude of modulated tone $n$ by
			\begin{equation}\label{eq:wf}
				s_{\mathrm{I}, n} = \sqrt{2\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}
			\end{equation}
			where $\lambda$ is chosen to satisfy the power constraint $\lVert{\boldsymbol{s}_I}\rVert^2 / 2 \le P$. The closed-form solution can be obtained by iterative power allocation \cite{Tse2005}, and the details are omitted here. On the other hand, SMF was proposed in \cite{Clerckx2017} as a suboptimal WPT resource allocation scheme that assigns the amplitude of sinewave $n$ by
			\begin{equation}\label{eq:smf}
				s_{\mathrm{P}, n} = \sqrt{\frac{2 P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha
			\end{equation}
			where the scaling ratio $\alpha \ge 1$ is given and can be adjusted to exploit the rectifier nonlinearity and frequency selectivity. When the receiver works in TS mode, there is no superposition in the suboptimal waveform design. Modulated waveform with amplitude \eqref{eq:wf} is used in the data session while multisine waveform with amplitude \eqref{eq:smf} is used in the energy session. When the receiver works in PS mode, we jointly design the combining ratio $\delta$ with the splitting ratio $\rho$, and assign the superposed waveform amplitudes as
			\begin{align}
				s_{\mathrm{I}, n} &= \sqrt{2(1 - \delta)\left(\lambda - \frac{\sigma_n^2}{P \lVert{\boldsymbol{h}_n}\rVert^2}\right)^+}, \label{eq:s_i}\\
				s_{\mathrm{P}, n} &= \sqrt{\frac{2 \delta P}{\sum_{n=1}^N \lVert{\boldsymbol{h}_n \rVert^{2 \alpha}}}}\lVert{\boldsymbol{h}_n}\rVert^\alpha. \label{eq:s_p}
			\end{align}
			Besides, minor modifications are required for passive beamforming to accommodate both low-complexity waveform schemes. To achieve the WIT point (i.e., $\eta=\rho=0$), the rate \eqref{eq:R_irs} instead of the DC current \eqref{eq:I_irs_approx} should be maximized. To achieve any non-WIT point (i.e., $I \ne 0$), the rate constraint \eqref{co:irs_rate} should be dropped as the R-E region is instead characterized by varying either $\eta$ or $\delta$ and $\rho$. The Modified-SCA (M-SCA) Algorithm~\ref{al:m_sca} summarizes the modified passive beamforming design when the receiver works in PS mode. The proofs of SDR tightness and local optimality are similar to Appendices~\ref{ap:relaxation} and \ref{ap:sca} thus omitted here. Compared with Algorithm~\ref{al:sca}, the rate constraint \eqref{co:irs_rate} is dropped and each SDP in Algorithm~\ref{al:m_sca} involves $(L+1)$ linear constraints. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:m_sca} is $\mathcal{O}\left(I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{M-SCA}}$ denotes the number of M-SCA iterations \cite{Luo2010}.

@@

		\begin{subsection}{Block Coordinate Descent}
			Based on the direct and cascaded CSIT, we iteratively update the passive beamforming $\boldsymbol{\phi}$ by Algorithm~\ref{al:sca}, the active precoder $\boldsymbol{b}_{\mathrm{I/P},n}$, $\forall n$ by equation \eqref{eq:b_n}, and the waveform amplitude $\boldsymbol{s}_{\mathrm{I/P}}$ and splitting ratio $\rho$ by Algorithm~\ref{al:gp}, until convergence. The steps are summarized in the BCD Algorithm~\ref{al:bcd}, which achieves local optimality with exponential computational complexity.

			\begin{algorithm}[!t]
				\caption{BCD: Waveform, Beamforming and Splitting Ratio.}
				\label{al:bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\bar{R},\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)},\rho^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)},\rho^{(i-1)}$ by Algorithm~\ref{al:sca}
						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Get $\boldsymbol{s}_{\mathrm{I/P}}^{(i)},\rho^{(i)}$ by Algorithm~\ref{al:gp}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $I^{(i)}$ by \eqref{eq:I_waveform}
					\Until $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)},\rho^{\star}=\rho^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star},\rho^{\star}$
				\end{algorithmic}
			\end{algorithm}

@@

			\begin{proof}\label{pf:bcd}
				See Appendix~\ref{ap:bcd}
			\end{proof}

			For the low-complexity design, when the receiver works in PS mode, we instead obtain the phase shift by Algorithm~\ref{al:m_sca} and the waveform amplitude by \eqref{eq:s_i} and \eqref{eq:s_p}. The steps are summarized in the Low Complexity-BCD (LC-BCD) Algorithm~\ref{al:lc_bcd}. Given a solution accuracy $\epsilon_{\mathrm{IPM}}$ for the interior-point method, the computational complexity of Algorithm~\ref{al:lc_bcd} is $\mathcal{O}\left(I_{\mathrm{LC-BCD}}I_{\mathrm{M-SCA}}(L+1)^{4.5} \log(\epsilon_{\mathrm{IPM}}^{-1})\right)$, where $I_{\mathrm{LC-BCD}}$ denotes the number of LC-BCD iterations \cite{Luo2010}.

			\begin{algorithm}[!t]
				\caption{LC-BCD: Waveform and Beamforming.}
				\label{al:lc_bcd}
				\begin{algorithmic}[1]
					\State \textbf{Input} $\beta_2,\beta_4,\boldsymbol{h}_{\mathrm{D},n},\boldsymbol{V}_{n},P,\sigma_n,\delta,\rho,\epsilon$, $\forall n$
					\State \textbf{Initialize} $i \gets 0$, $\boldsymbol{\phi}^{(0)},\boldsymbol{b}_{\mathrm{I/P},n}^{(0)},\boldsymbol{s}_{\mathrm{I/P}}^{(0)}$, $\forall n$
					\State Set $\boldsymbol{w}_{\mathrm{I/P},n}^{(0)}$, $\forall n$ by \eqref{eq:w}
					\Repeat
						\State $i \gets i + 1$
						\State Get $\boldsymbol{\phi}^{(i)}$ based on $\boldsymbol{w}_{\mathrm{I/P}}^{(i-1)}$ by Algorithm~\ref{al:m_sca}
						\State Update $\boldsymbol{h}_n^{(i)},\boldsymbol{b}_n^{(i)}$, $\forall n$ by \eqref{eq:h_n}, \eqref{eq:b_n}
						\State Update $\boldsymbol{s}_{\mathrm{I}}^{(i)},\boldsymbol{s}_{\mathrm{P}}^{(i)}$ by \eqref{eq:s_i}, \eqref{eq:s_p}
						\State Update $\boldsymbol{w}_{\mathrm{I/P},n}^{(i)}$, $\forall n$ by \eqref{eq:w}
						\State Compute $R^{(i)},I^{(i)}$ by \eqref{eq:R_waveform}, \eqref{eq:I_waveform}
					\Until $\lvert R^{(i)} - R^{(i-1)} \rvert \le \epsilon$ or $\lvert I^{(i)} - I^{(i-1)} \rvert \le \epsilon$
					\State Set $\boldsymbol{\phi}^{\star}=\boldsymbol{\phi}^{(i)},\boldsymbol{w}_{\mathrm{I/P}}^{\star}=\boldsymbol{w}_{\mathrm{I/P}}^{(i)}$
					\State \textbf{Output} $\boldsymbol{\phi}^{\star},\boldsymbol{w}_{\mathrm{I}}^{\star},\boldsymbol{w}_{\mathrm{P}}^{\star}$
				\end{algorithmic}
			\end{algorithm}
		\end{subsection}
	\end{section}

@@

			By applying SDR, problem~\eqref{ob:irs_equivalent}--\eqref{co:irs_equivalent_sd} is convex w.r.t. $\boldsymbol{\Phi}$ and satisfies the Slater's condition \cite{Boyd2004}, thus strong duality holds. The corresponding Lagrangian function at iteration $i$ is given by \eqref{eq:lagrangian}, where $\mu$, $\boldsymbol{\nu}$, $\boldsymbol{\Upsilon}$ denote respectively the scalar, vector and matrix Lagrange multiplier associated with constraint~\eqref{co:irs_equivalent_rate}, \eqref{co:irs_equivalent_modulus} and \eqref{co:irs_equivalent_sd}, and $\zeta$ collects all terms irrelevant to $\boldsymbol{\Phi}^{(i)}$.
